Suppressor tRNAs (sup-tRNAs) have emerged as a promising tool for correcting nonsense mutations associated with various genetic disorders \cite{albers_engineered_2023}. These mutations, caused by premature stop codons, can result in the loss of functional proteins, making sup-tRNAs a key therapeutic strategy to restore protein synthesis by decoding these stop codons. The design and application of sup-tRNAs, however, are hindered by the time-consuming and costly nature of traditional methods such as random mutagenesis and anticodon modification. Moreover, these approaches often lack systematic evaluation frameworks and accessible visualization tools, which are essential for optimizing and refining sup-tRNA designs.

To address these challenges, we developed iSEE-tRNA, an integrated web server designed to streamline the generation, evaluation, and visualization of engineered sup-tRNAs. By incorporating artificial intelligence (AI)-based tRNA generation, iSEE-tRNA leverages curated datasets of natural and engineered sup-tRNAs, utilizing the RFamGen algorithm to automatically generate novel tRNA sequences capable of decoding stop codons \cite{sumi_deep_2024}. Furthermore, the platform provides a multi-dimensional evaluation pipeline that ensures the functional success of sup-tRNAs by assessing key criteria such as stop codon recognition, structural integrity, identity elements for aminoacylation, and interaction with elongation factors. This systematic evaluation process guarantees that the generated sup-tRNAs meet the necessary requirements for effective translation.

In addition to these features, iSEE-tRNA offers an intuitive visualization interface powered by advanced tools like R2DT and AlphaFold3, allowing researchers to visualize and refine the secondary and tertiary structures of their engineered tRNAs. This user-friendly visualization aids in the validation of tRNA designs, enabling researchers to optimize their sequences before experimental implementation. Overall, iSEE-tRNA provides a comprehensive and accessible solution for the efficient design of sup-tRNAs, reducing both time and cost, while enhancing the accuracy and applicability of sup-tRNA engineering in genetic code expansion and tRNA therapeutics \cite{tang_recent_2022, shandell_genetic_2021}.


